Восстановление многогранника по набору его теневых контуров \\ Обзор материалов и план работы

### 2014-01-10 Documentation/i.palachev/Thesis/ReportAboutReconstruction/i.palachev_ReportAboutReconstruction.tex
[DOC] thesis: try to use thmtools package

\documentclass[a4paper,12pt, titlepage]{article} 
% пакет для задания полей страницы командой \geometry :
\usepackage{geometry}
\geometry{left=3cm,right=1.5cm,top=2cm,bottom=2cm}
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel}
\usepackage{amsmath}
%\usepackage{amsthm}
%\usepackage{cmap}
\usepackage{indentfirst}
\usepackage{a4wide,amssymb}
%\usepackage[pdftex]{graphicx}
%\usepackage[pdftex]{graphics}
%\usepackage{wrapfig}
%\linespread{1.3}               % полтора интервала. Если 1.6, то два интервала
\pagestyle{plain}               % номерует страницы

@@

@@

@@

\begin{flushleft}
\textbf{Определение}. Будем называть \textbf{опорной функцией} выпуклого тела
$K \subset \mathbb{R}^{n}$ следующую функцию 
$h_{K}: \mathbb{R}^{n} \to \mathbb{R}_{+}$:

$$h_{K}(u) = \max \limits_{x \in K}(x, u)$$
\end{flushleft}

>>>>

% Copyright (c) 2009-20134 Ilya Palachev <iliyapalachev@gmail.com>
% This document contains the report about reconstruction of convex sets.

% Declare the class of document: size of paper, size of font, and etc.
% Type of the document is "article".
\documentclass[a4paper, 12pt, titlepage]{article}

% Package that enables setting the size of free spaces at the border of the 
% page with the command  \geometry :
\usepackage{geometry}
\geometry {
   left=3cm,
   right=1.5cm,
   top=2cm,
   bottom=2cm
}

\usepackage[utf8]{inputenc}

\usepackage[english,russian]{babel}

\usepackage{amsmath}

%\usepackage{cmap}

\usepackage{indentfirst}

\usepackage{a4wide,amssymb}

%\usepackage[pdftex]{graphicx}

%\usepackage{wrapfig}

%\linespread{1.3}               % полтора интервала. Если 1.6, то два интервала
\pagestyle{plain}               % номерует страницы

@@

% Package that enables usage of theorems and definition designed in a 
% standard way.
% http://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}

% The thmtools bundle is a collection of packages that is designed to provide an
% easier interface to theorems, and to facilitate some more advanced tasks
% http://texdoc.net/texmf-dist/doc/latex/thmtools/thmtools.pdf
\usepackage{thmtools}

@@

% Enable smart references to theorems (this was writte according to the manual 
% of "thmtools").
\usepackage {
   nameref,   % for command \nameref
   % hyperref,  % for command \autoref
   % (Above line was commented, because hyperref has been already enabled)
   % n.b. \Autoref is defined by thmtools
   cleveref,  % for command \cref
   % n.b. cleveref after! hyperref
}

% Declare the standard theorem environment that will be used throughout the
% article.
\declaretheorem[name=Theorem,
   refname={theorem,theorems},
   Refname={Theorem,Theorems}]{SmartTheorem}

\declaretheorem[name=Definition,
   refname={definition,definitions},
   Refname={Definition,Definitions}]{SmartDefinition}

@@

\begin{SmartDefinition}[Опорная функция]
\label{def/support-function}
Будем называть \textbf{опорной функцией} выпуклого тела
$K \subset \mathbb{R}^{n}$ следующую функцию 
$h_{K}: \mathbb{R}^{n} \to \mathbb{R}_{+}$:

$$h_{K}(u) = \max \limits_{x \in K}(x, u)$$
\end{SmartDefinition}
